---
title: "Shiny App Reproducible Pitch"
author: "Choi Seungyong"
date: '2021 11 21'
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Background of this project

I am a time traveller and I am going to go back to 1973.
And I am planning to visit my grandma in Dallas by car.
So I need a car to drive and there were so many cars at that time too.
So It's hard to make up my mind choosing a car for travelling

Using the `mtcars` dataset I am going to compare cars from the table

Milage, horsepower, Quarter Mile Time, cylinders, Transmission, Gears could be important things to choose

## Application Overview

The table will be made with variables like milage, gross horsepower, quarter mile time, number of cylinders, transmission type, number of gears

And variables will be entered by bars and radio buttons 

Finally the table will be made with how you choose variables

## Slide with Complete Reporting Application

Click the link below for the application.
https://seungyong-choi.shinyapps.io/data_product/

Click the link below complied project files on github repositaoy
https://github.com/gomdalae/Coursera_Developing_Data_Products_Week_4_Assignment

## Data Overview

The data used for this application is the "mtcars" dataset, which is part of base R. "mtcars' has 32 rows and 11 variables
```{r, message=FALSE}
head(mtcars)
```